Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-22 awipev-CO2.Rmd
added section Traitement des variables

dygraph(sal_xts, group = "awipev", main="Salinities (in situ CTD, all depths + FB)", ylab="Salinity") %>%
      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "CTD") %>%
            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "FB") %>%

>>>>

dygraph(sal_xts, group = "awipev", main="Salinity FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 1, label = "sal_fb") %>%
            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "sal_fb") %>%
